### 2020-01-31 abstract_file.tex
mostly section 3, but touched every section

In many applications,
% of machine learning and artificial intelligence, 
one must work with models that have been trained by someone else.
For such \emph{pretrained models}, one typically does not have access to training data or test data, and one does not know the details of how the models were built, the specifics of the data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized, etc.
Here, we present and evaluate quality metrics for pretrained neural network models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
Using the publicly-available \emph{WeightWatcher} tool, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision and natural language processing.
We find that norm-based metrics do a reasonably good job at predicting quality trends in well-trained models, i.e., they can be used to discriminate between ``good-better-best.'' 
On the other hand, for models that may not be well-trained (which, arguably is the point of needing metrics to evaluate the quality of pretrained models), i.e., when we want to distinguish ``good-bad,'' norm-based metrics can qualitatively fail. 
We also find that HT-SR metrics do much better, quantitatively better for at discriminating good-better-best and qualitatively better at discriminating good-bad.
HT-SR metrics can also be used to characterize fine-scale properties of models, e.g., understanding layer-wise \emph{correlation flow}, and evaluate post-training modifications such as model distillation and model improvement.

>>>>

In many applications,
% of machine learning and artificial intelligence, 
one must work with models that have been trained by someone else.
For such \emph{pretrained models}, one typically does not have access to training data or test data, and one does not know the details of how the models were built, the specifics of the data that were used to train the model, what was the loss function or hyperparameter values, how precisely the model was regularized, etc.
Here, we present and evaluate quality metrics for pretrained neural network models at scale.
%%Our metrics are drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as Heavy-Tailed Random Matrix Theory (HT-RMT), as used in the recently-developed Theory of Heavy-Tailed Self Regularization (e.g., fitted power law metrics used to characterize the degree of strong correlations in trained models).
The most promising are metrics drawn from traditional statistical learning theory (e.g., norm-based capacity control metrics) as well as metrics (e.g., fitted power law metrics used to characterize the degree of strong correlations in a system) derived from the recently-developed Theory of Heavy-Tailed Self Regularization (HT-SR).
Using the publicly-available \emph{WeightWatcher} tool, we analyze hundreds of publicly-available pretrained models, including older and current state-of-the-art models in computer vision and natural language processing.
We find that norm-based metrics do a reasonably good job at predicting quality trends in well-trained models, i.e., they can be used to discriminate between ``good-better-best.'' 
On the other hand, for models that may not be well-trained (which, arguably is the point of needing metrics to evaluate the quality of pretrained models), i.e., when we want to distinguish ``good-bad,'' norm-based metrics can qualitatively fail. 
We also find that HT-SR metrics do much better, quantitatively better at discriminating good-better-best and qualitatively better at discriminating good-bad.
HT-SR metrics can also be used to characterize fine-scale properties of models, e.g., understanding layer-wise \emph{correlation flow}, and evaluate post-training modifications such as model distillation and model improvement.

### 2020-01-31 appendix.tex
mostly section 3, but touched every section

\section{Methods}
\label{sxn:methods}

Let us write the Energy Landscape (or optimization function, parameterized by $\mathbf{W}_{l}$s and $\mathbf{b}_{l}$s) for a typical DNN with $L$ layers, with activation functions $h_{l}(\cdot)$, and with $N\times M$ weight matrices $\mathbf{W}_{l}$ and biases $\mathbf{b}_{l}$, as:
\begin{equation}
E_{DNN}=h_{L}(\mathbf{W}_{L}\times h_{L-1}(\mathbf{W}_{L-1}\times h_{L-2}(\cdots)+\mathbf{b}_{L-1})+\mathbf{b}_{L})  .
\label{eqn:dnn_energy}
\end{equation}
We assume we are given several pretrained Deep Neural Networks (DNNs), e.g., as part of an architecture series.
The models have been trained on (unspecified and unavailable) labeled data $\{d_{i},y_{i}\}\in\mathcal{D}$, using Backprop, by minimizing some (also unspecified and unavailable) loss function $\mathcal{L}()$. 
We expect that most well-trained, production-quality models will employ one or more forms of on regularization, such as Batch Normalization, Dropout, etc., and many will also contain additional structure such as Skip Connections, etc. 
Here, we will ignore these details, and will focus only on the weight matrices.

\paragraph{DNN Quality Metrics.}

Each DNN layer contains one or more layer 2D weight matrices $\mathbf{W}_{L}$, and/or 2D feature maps $\mathbf{W}_{i,L}$ extracted from 2D Convolutional layers. 
(For notational convenience, we may drop the $i$ and/or $i,l$ subscripts below.) 
%
\charles{hard to confer on this.  I tried to state this as simply as possible.  We have never stated this before, and I think its going to be confusing.  We at least need to explain why we are looking at the average log norm. Otherwise we are forcing the reader to look back, and the paper is hard to read as a standalone entity. }
\michael{
XXX.  PROBABLY WE DO NOT WANT THE FOLLOWING.  INSTEAD, JUST PRESENT METRICS AND POINT TO PREVIOUS PAPERS FOR JUSTIFICATION.  E.G., WE DONT WANT TO JUSTIFY THE IMPLICIT STATISTICAL INDEPENDENCE ASSUMPTION HERE.  IF OKAY, JUST DELETE THIS RED BLOCK.
We assume the layer weight matrices are statistically independent, allowing us to estimate the Complexity $\mathcal{C}$, or test accuracy, with a standard Product Norm, which resembles a data dependent VC complexity
\begin{equation}
\mathcal{C}\sim\Vert\mathbf{W}_{1}\Vert\times\Vert\mathbf{W}_{2}\Vert\cdots\Vert\mathbf{W}_{L}\Vert ,
\end{equation}
where $\mathbf{W}$ is an $(N\times M)$ weight matrix, with $N\ge M$, and 
 $\Vert\mathbf{W}\Vert$ is a matrix norm.   We will actually compute the log Complexity, which takes the form 
of an Average Log Norm:
\begin{eqnarray*}
\log\mathcal{C} &\sim& \log\Vert\mathbf{W}_{1}\Vert+\log\Vert\mathbf{W}_{2}\Vert\cdots\log\Vert\mathbf{W}_{L}\Vert
\end{eqnarray*}
}
%
We have examined a large number of possible quality metrics.
The best performing metrics (recall that we can only consider metrics that do not use training/test data) depend on the norm and/or spectral properties of weight matrices, $\mathbf{W}$.%
\footnote{We do not use intra-layer information from the models in our quality metrics, but as we will describe our metrics can be used to learn about }
We consider the following metrics.
\begin{itemize}
\item 
Frobenius Norm: $\Vert\mathbf{W}\Vert^{2}_{F}=\Vert\mathbf{W}\Vert^{2}_{2}=\sum_{i,j}w^{2}_{i,j} = \sum_{i=1}^{M} \lambda_{i}^{2}$
\michael{Do we use norm or log norm, here and with other norms.  Worth being very explicit and very consistent.}
\item 
Spectral Norm: $\Vert\mathbf{W}\Vert_{\infty}=\lambda_{max}$
\michael{We should probably call the spectral norm $\Vert\mathbf{W}\Vert_{2}$, or change Frob norm notation and have an explicit remork.  Let's decide.}
\item 
Weighted Alpha Metric: $\hat{\alpha}=\alpha\log\lambda_{max}$
\item 
$\alpha$-Norm (or $\alpha$-Shatten Norm): $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}=\sum_{i=1}^{M}\lambda_{i}^{\alpha}$,
\michael{Be clear about how we average this across layers.}
\end{itemize}
The first two metrics are well-known in ML.
The last two deserve special mention.
For all these metrics, $\lambda_{i}$ is the $i^{th}$ eigenvalue of the \emph{Empirical Correlation Matrix},
$ %% $$
\mathbf{X}=\mathbf{W}^{T}\mathbf{W} ,
$ %% $$
and so $\lambda_{max}$ is the maximum eigenvalue of $\mathbf{X}$. 
(These eigenvalues are the squares of the singular values $\sigma_{i}$ of $\mathbf{W}$, i.e., $\lambda_{i}=\sigma^{2}_{i}$.)
For the last two metrics, the exponent $\alpha$ is the power law exponent that arises in the recently-developed \emph{Theory of Heavy Tailed Self Regularization (HT-SR)}~\cite{MM18_TR, MM19_HTSR_ICML, MM20_SDM}.
Operationally, $\alpha$ is determined by using the publicly-available \emph{WeightWatcher} tool (\cite{weightwatcher_package}) to fit the Empirical Spectral Density (ESD) of $\mathbf{X}$, i.e., a histogram of the eigenvalues, call it $\rho(\lambda)$, to a truncated power law
\begin{equation}
\rho(\lambda)\sim\lambda^{\alpha},\;\;\lambda\le\lambda_{max}  .
\end{equation}
\michael{We need to be clear that this is a truncated power law fit and that $\lambda_{max}$ comes from that and not the largest empirical eigenvalue.}
The Weighted Alpha Metric was introduced previously~\cite{MM20_SDM}, where (on a much smaller set of data than we consider here) it was shown to correlate well with the trends in reported test accuracies of pretrained DNNs.
Based on this, here we introduce and evaluate the $\alpha$-Norm metric.
One would expect $\hat{\alpha}$ to approximate the log $\alpha$-Norm very well for $\alpha < 2$ and reasoably well for $\alpha\in[2,5]$~\cite{MM20_unpub_work}.

\michael{Need to say that such large $\alpha$ values don't mean much.}

\michael{Need to highlight difference between $\alpha$ and $\hat{\alpha}$.}

\paragraph{Spectral Analysis of Convolutional 2D Layers.}

There is some ambiguity in performing spectral analysis on Convolutional 2D (Conv2D) layers.  
A Conv2D layer can be represented as a 4-index tensor of dimension $(w,h,in\_ch,out\_ch)$, specified by an $(w\times h)$ filter (or kernel) and $in\_ch$ / $out\_ch$ input / output channels, respectively (usually $in\_ch\le out\_ch$). 
Typically, $w=h=k$,  giving $(k\times k)$ tensor slices, or \emph{pre-Activation Maps} $\mathbf{W}_{i,L}$ of dimension $(in\_ch\times out\_ch)$ each. 
%
There are at least three different approaches that have been advocated for applying the Singular Values Decomposition (SVD) to an Conv2D layer:
run an SVD on each of the pre-Activation Maps $\mathbf{W}_{i,L}$, yielding $(k\times k)$ sets of $M$ singular values; 
stack the feature maps into a single rectangular matrix of, say, dimension $((k\times k\times out\_ch)\times in\_ch)$, yielding $in\_ch$ singular values;
compute the 2D Fourier Transform (FFT) for each of the $(in\_ch, out\_ch)$ pairs, and run SVD on the resulting Fourier coeffients~\cite{Long2019}, leading to $\sim(k\times in\_ch\times out\_ch)$ non-zero singular values.
Each method has tradeoffs.  
In principle, the third method is mathematically sound, but it is computationally expensive. 
For our analysis, because we are performing tens of thousands of calculations, we select the first method, which is numerically the fastest and is easiest to reproduce.%
\footnote{We provide a Google Colab notebook where all results can be reproduced, with the option to redo the calculations with the third option for the SVD of the Conv2D.}

@@

\paragraph{Normalization of Empirical Matrices.}  
Normalization is an important, if underappreciated, practical issue.
Importantly, the normalization of weight matrices does \emph{not} affect the Power Law fits because the Heavy Tailed exponent $\alpha$ (as well as other metrics such as the Stable Rank and MP Soft Rank~\cite{MM18_TR,MM19_HTSR_ICML}) is scale-invariant.
Norm-based metrics, however, do depend strongly on the scale of the weight matrix.
Typically, to apply RMT, we would usually define Correlation Matrix with $1/N$ normalization and assume that the variance of $\mathbf{X}$ is either unity or a known constant.% 
\footnote{For formal proofs of Heavy Tailed results, one typically needs a different normalization such as $1/N^{1-\alpha}$.}
Pretrained DNNs are typically initialized with random weight matrices $\mathbf{W}_{0}$, with the variance already normalized to $\sqrt{1/N}$, or some variant of this, e.g., the Glorot/Xavier normalization~\cite{GloRot}, or a $\sqrt{2/Nk^2}$ normalization for Convolutional 2D Layers.
We do not have conrol over the final empirical normalization of these models; and we do \emph{not} normalize (or renormalize) the Empirical Correlation Matrices, i.e., we use them as-is.
The only exception to this is that we do rescale the Conv2D pre-Activation Maps $\mathbf{W}_{i,L}$ by $k/\sqrt{2}$ so that they are on the same scale as the Linear layers.

\michael{MOVE TO LATER: COMMENT ON HOW LOG NORM first and last layers behave, maybe somewhere else.}

\michael{CMOVE TO LATER: OMMENT ON HOW LOG PORM  for GPT includes unusually high alpha, not meaningful other than to show the trend.}

\paragraph{The WeightWatcher Tool.}

We compute the metrics using the WeightWatcher tool (version 0.2.7), and we provide Jupyter notebooks in the github repo for this paper~\cite{repo}, making the results fully reproducible.

\michael{XXX.  FEW SENTENCES ABOUT REPRODUCIBILITY MORE GENERALLY HERE.}

>>>>

\section{Appendix}

XXX.  APPENDIX.

\michael{I put this here for now as a placeholder.  Where to put it.  Maybe in a discussion/conclusion if there is space.}

@@

### 2020-01-31 background.tex
edit text
mostly section 3, but touched every section

XXX.
Cite our stuff:
\cite{MM17_TR},
\cite{MM18_TR},
\cite{MM19_HTSR_ICML},
\cite{weightwatcher_package}
\cite{MM19_KDD},
\cite{MM20_SDM},
\cite{MM20_unpub_work}.C
Cite also Ganguli review and maybe other stuff.
\charles{Gangulis work is not really close to what we are doing, although I get the politics.   The closest useful work would be the older work by Bouchaud and Potters, which discusses the statisical mechanics of heavy tailed and strongly correlated systems form the 90s}

XXX.
Distinguish between what we will call a
\emph{phenomenological theory}
(that describes empirical relationship of phenomena to each other, in a way which is consistent with fundamental theory, but is not directly derived from that theory)
and what can be called a 
\emph{first principles theory} 
(that is applicable to tiny things but has no hope of scaling up).
\charles{it is the oppposite...ab initio theory scales quite well...it is the spherical cow models of physics and ML that do not scale. What we have is a semi-empirical theory.  We use real theory, but require empirical input, at least in the new stat mech work.  What we have introduced is a phenomenology, which to me is different from a semi-empirical or phenomenological theory  }
\footnote{In most areas where there are complex highly-engineered systems (beyond complex AI/ML systems), one used phenomenological theory rather than first principles theory.  For example, one does not try to solve the Schr\"odinger equation if one is interested in building a bridge or an airplane.}

@@

\paragraph{Practical problems poorly addressed by theory.}
There are many very practical problems in ML that are poorly addressed by existing theory and that either motivated our work or should be addressable by our techniques.
Here are several.
\begin{itemize}
\item
\textbf{Lack of accuracy metrics.}
\item
\textbf{Lack of data.}
\item
XXX. LACK OF SOMETHING ELSE.
\end{itemize}
Importantly, there are many examples in ML where (as a practical matter) there is no reliable notion of accuracy, e.g., when generating fake text, when developing self driving cars, or creating realistic chatbots.\footnote{i.e. current chatbots use perplexity as a proxy for passing a Turing test}
%, and when distilling a reliable model in some way to obtain comparable training/test quality but that damages the model in some other subtle way. 
%\michael{That last example is awkward.  It would be good to have a better example and plant seeds for model distillation elsewhere.}

>>>>

XXX.
Cite our stuff:
\cite{MM17_TR},
\cite{MM18_TR},
\cite{MM19_HTSR_ICML},
\cite{weightwatcher_package}
\cite{MM19_KDD},
\cite{MM20_SDM},
\cite{MM20_unpub_work}.
Cite also Ganguli review and maybe other stuff.
\charles{Gangulis work is not really close to what we are doing, although I get the politics.   The closest useful work would be the older work by Bouchaud and Potters, which discusses the statisical mechanics of heavy tailed and strongly correlated systems form the 90s}
\michael{Yes on both.}

XXX.
Distinguish between what we will call a
\emph{phenomenological theory}
(that describes empirical relationship of phenomena to each other, in a way which is consistent with fundamental theory, but is not directly derived from that theory)
and what can be called a 
\emph{first principles theory} 
(that is applicable to tiny things but has no hope of scaling up).
\charles{it is the oppposite...ab initio theory scales quite well...it is the spherical cow models of physics and ML that do not scale. What we have is a semi-empirical theory.  We use real theory, but require empirical input, at least in the new stat mech work.  What we have introduced is a phenomenology, which to me is different from a semi-empirical or phenomenological theory  }
\michael{Let's touch base to get this right.}
\footnote{In most areas where there are complex highly-engineered systems (beyond complex AI/ML systems), one used phenomenological theory rather than first principles theory.  For example, one does not try to solve the Schr\"odinger equation if one is interested in building a bridge or an airplane.}

@@

\paragraph{Practical problems poorly addressed by theory.}
There are many very practical problems in ML that are poorly addressed by existing theory and that either motivated our work or should be addressable by our techniques.
Here are several.
\begin{itemize}
\item
\textbf{Simplicity, or lack of,  accuracy metrics.}
XXX.
\item
\textbf{Information leakage in the production pipeline.}
XXX.
\item
\textbf{Cost of acquring labeled data.}
XXX.
\end{itemize}
Importantly, there are many examples in ML where (as a practical matter) there is no reliable notion of accuracy, e.g., when generating fake text, when developing self driving cars, or when creating realistic chatbots.%
\footnote{For example, current chatbots use perplexity as a proxy for passing a Turing test.}
%, and when distilling a reliable model in some way to obtain comparable training/test quality but that damages the model in some other subtle way. 
%\michael{That last example is awkward.  It would be good to have a better example and plant seeds for model distillation elsewhere.}

### 2020-01-31 cv_models.tex
mostly section 3, but touched every section

In this section, we examine the quality metrics described in Section~\ref{sxn:methods} for several CV model architecture series.
This includes the VGG, ResNet, and DenseNet series of models, each of which consists of several pretrained DNN models, trained on the full ImageNet~\cite{imagenet} dataset, and each of which is distributed with the current opensource pyTorch framework (version 1.4)~\cite{pyTorch}.
This also includes results for a larger set of ResNet models, trained on the ImageNet-1K dataset~\cite{imagenet1k}, provided on the OSMR ``Sandbox for training convolutional networks for computer vision''~\cite{osmr}, which we call the ResNet-1K series.
We use our quality metrics to understand the gross properties of these models, comparing and contrasting the three (of four, if ResNet-1K is a distinct series) model series.
We also use our metrics to understand more fine-scale properties of these models as a function of model depth.
\michael{And mention distillation, if we include that in this section.}

@@

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ Alpha-Norm ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of quality metrics versus reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  
             XXX Plots will be updated and replaced. 
             \michael{Figures are unreadable, can we make fonts bigger, etc.}
            }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet ]{
        %\includegraphics[width=4.2cm]{img/ResNet_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        %\includegraphics[width=4.5cm]{img/ResNet-1K_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \qquad
    \subfigure[ DenseNet ]{
        %\includegraphics[width=4.4cm]{img/DenseNet_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/DenseNet_logpnorm_accs.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm versus reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models.}
    \label{fig:cv2-accuracy}
\end{figure}

\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|c|}
\hline
   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
 Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
\hline
 VGG & 6 & 0.56 & 0.53 & 0.48 & 0.42  \\
 ResNet & 5 & 0.9 & 1.4 & 0.61 & 0.66  \\
 ResNet-1K & 19 & 2.4 & 3.6 & 1.8 & 1.9  \\
 DenseNet & 4 & 0.3 & 0.26 & 0.16 & 0.21 \\
\hline
\end{tabular}
\end{center}
\caption{RMSE for linear fits (smaller is better) of quality metrics to Reported Top1 Test Error (\cite{XXX-GIVE-REFS-AGAIN}\michael{Give refs again.}) for all pretrained models in the architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. \michael{Do we want Frob norm squared.} }
\label{table:cv-models}
\end{table}

\paragraph{Correlation Flow in CV Models.}

@@

    \subfigure[ VGG ]{
        \includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        \includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        \includegraphics[width=4.5cm]{img/DenseNet_fnl_alpha_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{PL exponent $\alpha$ versus layer for VGG, ResNet-1K, and DenseNet models.  Y axes on each plot are different.  ResNet-1K exhibits very different and much more stable behavior, which we interpret in the text as a \emph{correlation flow} across the layers.  }
    \label{fig:vgg-alpha-layers}
\end{figure}

@@

\paragraph{Behavior on Less Thoroughy Studied CV Models.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      %\includegraphics[width=3.7cm]{img/resnet4d_maxev.png}
      \includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dalpha}
   }
   \qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      %\includegraphics[width=3.7cm]{img/resnet4d_alphas.png}
      \includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dmaxev}
   }
   \caption{
     Analysis of ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
     Comparison of individual layer $\mathbf{W}_{l}$ maximum eigenvalues ($\lambda_{max}$, or Spectral Norms) and  
     PL exponent $\alpha$, between baseline (green) and fine-tuned (red)  pre-trained models.   
           }
   \label{fig:resnet204D5L}
\end{figure}

>>>>

\michael{Need to say that such large $\alpha$ values don't mean much.}

\michael{Need to highlight difference between $\alpha$ and $\hat{\alpha}$.}

In this section, we examine the quality metrics described in Section~\ref{sxn:methods} for several CV model architecture series.
This includes the VGG, ResNet, and DenseNet series of models, each of which consists of several pretrained DNN models, trained on the full ImageNet~\cite{imagenet} dataset, and each of which is distributed with the current opensource pyTorch framework (version 1.4)~\cite{pyTorch}.
This also includes results for a larger set of ResNet models, trained on the ImageNet-1K dataset~\cite{imagenet1k}, provided on the OSMR ``Sandbox for training convolutional networks for computer vision''~\cite{osmr}, which we call the ResNet-1K series.

We use our quality metrics to perform \emph{coarse model analysis}, comparing and contrasting the three (or four, if ResNet-1K is a distinct series) model series, permitting us to understand the gross properties of these models. 
We also use our metrics to perform \emph{fine layer analysis}, permitting us to understand more fine-scale properties of these models as a function of model depth.

@@

\begin{figure}[t]
    \centering
    \subfigure[ Frobenius Norm, VGG ]{
        %\includegraphics[width=5cm]{img/VGG_lognorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_lognorm_accs.png}
        \label{fig:vgg-fnorm}
    }
    %\qquad
    \subfigure[ Spectral Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_spectralnorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_spectralnorm_accs.png}
        \label{fig:vgg-snorm}
    }
    %\qquad
    \subfigure[ Weighted Alpha, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_alpha_weighted_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_alpha_weighted_accs.png}
        \label{fig:vgg-walpha}
    }
    %\qquad
    \subfigure[ $\alpha$-Norm, VGG ]{
        %\includegraphics[width=4.9cm]{img/VGG_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/VGG_logpnorm_accs.png}
        \label{fig:vgg-pnorm}
    }
    \caption{Comparison of quality metrics versus reported test accuracy for pretrained VGG models, trained on ImageNet, available in pyTorch.  
             XXX Plots will be updated and replaced. 
             \michael{Figures are unreadable, can we make fonts bigger, etc.}
            }
    \label{fig:vgg-metrics}
\end{figure}

@@

    \subfigure[ ResNet, $\alpha$-Norm ]{
        %\includegraphics[width=4.2cm]{img/ResNet_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/ResNet_logpnorm_accs.png}
        \label{fig:resnet-accuracy}
    }
    \qquad
    \subfigure[ ResNet-1K, $\alpha$-Norm ]{
        %\includegraphics[width=4.5cm]{img/ResNet-1K_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/ResNet-1K_logpnorm_accs.png}
        \label{fig:resnet1k-accuracy}
    }
    \qquad
    \subfigure[ DenseNet, $\alpha$-Norm ]{
        %\includegraphics[width=4.4cm]{img/DenseNet_logpnorm_accs.png}
        \includegraphics[width=3.7cm]{img/DenseNet_logpnorm_accs.png}
        \label{fig:densenet-accuracy}
    }
    \caption{$\alpha$-Norm versus reported Top1 Error for  ResNet, ResNet-1K, and DenseNet models. The corresponding results for VGG are shown in Figure~\ref{fig:vgg-pnorm}.  }
    \label{fig:cv2-accuracy}
\end{figure}

\begin{table}[t]
\small
\begin{center}
%\begin{tabular}{|p{1in}|c|c|c|c|c|}
\begin{tabular}{|p{0.75in}|c|c|c|c|c|}
%\begin{tabular}{|l|c|c|c|c|c|}
\hline
%   &    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
% Series & \#Models   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}=\alpha\log\lambda_{max}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
        & Num.   & $\Vert\mathbf{W}\Vert_{F}$ & $\Vert\mathbf{W}\Vert_{2}$ & $\hat{\alpha}$ & $\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}$ \\
 Series & Models & Metric                     & Metric                     & Metric         & Metric                                   \\
\hline
 VGG & 6 & 0.56 & 0.53 & 0.48 & 0.42  \\
 ResNet & 5 & 0.9 & 1.4 & 0.61 & 0.66  \\
 ResNet-1K & 19 & 2.4 & 3.6 & 1.8 & 1.9  \\
 DenseNet & 4 & 0.3 & 0.26 & 0.16 & 0.21 \\
\hline
\end{tabular}
\end{center}
\caption{RMSE (smaller is better) for linear fits of quality metrics to Reported Top1 Test Error for pretrained models in each architecture series.  VGG, ResNet, and DenseNet were pretrained on ImageNet, and ResNet-1K was pretrained on ImageNet-1K. }
\label{table:cv-models}
\end{table}

\paragraph{Layer Analytics: Correlation Flow in CV Models.}

@@

    \subfigure[ VGG ]{
        %\includegraphics[width=4.5cm]{img/VGG_fnl_alpha_depth.png} 
        \includegraphics[width=3.7cm]{img/VGG_fnl_alpha_depth.png} 
                \label{fig:vgg-alpha-layers}
    }
    \qquad
    \subfigure[ ResNet-1K ]{
        %\includegraphics[width=4.5cm]{img/ResNet_fnl_alpha_depth.png} 
        \includegraphics[width=3.7cm]{img/ResNet_fnl_alpha_depth.png} 
        \label{fig:resnet-alpha-layer}
    }
    \qquad
    \subfigure[ DenseNet ]{
        %\includegraphics[width=4.5cm]{img/DenseNet_fnl_alpha_depth.png} 
        \includegraphics[width=3.7cm]{img/DenseNet_fnl_alpha_depth.png} 
        \label{fig:densenet-alpha-layer}
    }
    \caption{PL exponent $\alpha$ versus layer for VGG, ResNet-1K, and DenseNet models.  Y axes on each plot are different.  ResNet-1K exhibits very different and much more stable behavior across layers, which we interpret in the text as a \emph{correlation flow} across the layers.  }
    \label{fig:vgg-alpha-layers}
\end{figure}

@@

\paragraph{Layer Analytics: Behavior on Less Thoroughy Studied CV Models.}

@@

\begin{figure}[t]
   \centering
   \subfigure[$\lambda_{max}$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_maxev.png}
      \includegraphics[width=3.7cm]{img/resnet4d_maxev.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_maxev.png}
      \label{fig:resnet204Dalpha}
   }
   \qquad
   \subfigure[$\alpha$ for ResNet20 layers]{
      %\includegraphics[scale=0.14]{img/resnet4d_alphas.png}
      \includegraphics[width=3.7cm]{img/resnet4d_alphas.png}
      %\includegraphics[width=4.5cm]{img/resnet4d_alphas.png}
      \label{fig:resnet204Dmaxev}
   }
   \caption{
     Analysis of ResNet20, distilled with Group Regularization, as implemented in the \texttt{distiller} (4D\_regularized\_5Lremoved) pre-trained models.  
     Comparison of individual layer $\mathbf{W}_{l}$ maximum eigenvalues ($\lambda_{max}$, or Spectral Norms) and  
     PL exponent $\alpha$, between baseline (green) and fine-tuned (red)  pre-trained models.   
           }
   \label{fig:resnet204D5L}
\end{figure}
